Fictitious Play in Network Aggregative Games

### 2021-04-23 Documents/FP in NAGs/FPNAG.tex
minor edits

                We first show that a Nash
                Equilibrium exists and that Fictitious Play admits
                solutions in this setting. In particular, we study
                zero-sum games and show that Fictitious Play converges
                to a fixed point, which for a network without any self-loops
                corresponds to a Nash Equilibrium. In addition, we
                find that, for games which are not zero-sum, agents
                following Continuous Time Fictitious Play are able to
                achieve no regret.

		Finally, we explore the Fictitious Play algorithm
                through numerical simulations to understand how
                convergence rates depend on the network size and
                connectivity. We also show that it does not
                necessarily converge for more complex games and can,
                in fact, lead to more complex dynamics. In addition,
                we experiment the Fictitious Play algorithm on an
                agent based model for \ah{resource allocation? 
                voting?}. Finally, our experiments document how noise
                affects the convergence of fictitious play, whose
                theoretical analysis we point out as an interesting
                direction for future work.

@@

	The model we consider is that there is a set $\agentset = {1,
         \ldots , N}$ of agents who are connected through an underlying
        interaction graph. This graph is given by the tuple
        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
        the set of all pairs $(\mu, \nu) \in \agentset \times
        \agentset$ such that agent $\mu$ and agent $\nu$ are
        connected. Formally,

          \begin{definition}[Interaction Graph]
  Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset, \weightset))$ such that
  \begin{itemize}
  \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent $\mu$ is
        denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in
        \edgeset\}$.
    \item $\weightset \in M_N(\mathbb{R})$ is the weighted
        adjacency matrix whose elements $w^{\mu \nu}$ expresses the
        importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
  \end{itemize}
\end{definition}

	As a network game, each agent $\mu$ has an associated set of
        actions $\actionset{\mu}$ which has cardinality
        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
          we define them if we didn't introduce actions?}

        We can construct the \fb{unit-simplex ?} on the action
        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
        with which agent $\mu$ plays the action $i$. As such we
        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
        often referred to as $\mu$'s mixed strategy). Also associated
        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
        in which we use the standard notation $-\mu$ to refer to all
        agents other than $\mu$. Notice that this requires that each
        agent plays the same strategy against all of their neighbours.

	With all of the above definitions, we can formalise the
        network aggregative (NA) game:

	\begin{definition}[Network Aggregative Game]
		A Network Aggregative game is defined as the tuple $\Gamma =
        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$, where $\agentset$, $\edgeset$, $\weightset$ are as
        defined in the Interaction graph. $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
        actions and the utility function of agent $\mu$ respectively..
	\end{definition}

@@

	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
	Fictitious Play in continuous time.
%
	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and
		all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in
		BR_i(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
	\end{definition}

@@

	\begin{theorem}
		There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
		BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
	\end{theorem}

@@

	\subsection{Non-convergent examples}
	The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.

@@

	\subsection{Addition of Noise}

>>>>

                We first show that a Nash
                Equilibrium exists and that Fictitious Play admits
                solutions in this setting. In particular, we study
                zero-sum games and show that Fictitious Play converges
                to a fixed point, which for a simple \fb{define simple} network
                corresponds to a Nash Equilibrium. In addition, we
                find that, for games which are not zero-sum, agents
                following Continuous Time Fictitious Play are able to
                achieve no regret.

		Finally, we explore the Fictitious Play algorithm
                through numerical simulations to understand how
                convergence rates depend on the network size and
                connectivity. We also show that it does not
                necessarily converge for more complex games and can,
                in fact, lead to more complex dynamics. In addition,
                we experiment the Fictitious Play algorithm on an
                agent based model for (resource allocation?
                voting?). Finally, our experiments document how noise
                affects the convergence of fictitious play, whose
                theoretical analysis we point out as an interesting
                direction for future work.

@@

	The model we consider is that there is a set $\agentset = {1,
         \ldots , N}$ of agents who are connected through an underlying
        interaction graph. This graph is given by the tuple
        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
        the set of all pairs $(\mu, \nu) \in \agentset \times
        \agentset$ such that agent $\mu$ and agent $\nu$ are
        connected.
        \fb{
          \begin{definition}[Interaction Graph]
  Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset, \weightset))$ such that
  \begin{itemize}
  \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent $\mu$ is
        denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in
        \edgeset\}$.
    \item $\weightset \in M_N(\mathbb{R})$ is the weighted
        adjacency matrix whose elements $w^{\mu \nu}$ expresses the
        importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
  \end{itemize}
\end{definition}
}

	As a network game, each agent $\mu$ has an associated set of
        pure strategies $\actionset{\mu}$ which has cardinality
        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
          we define them if we didn't introduce actions?}

        Then we can construct the \fb{unit-simplex ?} on this action
        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
        with which agent $\mu$ plays the pure strategy $i$. As such we
        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
        often referred to as $\mu$'s mixed strategy). Also associated
        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
        in which we use the standard notation $-\mu$ to refer to all
        agents other than $\mu$. Notice that this requires that each
        agent plays the same strategy against all of their neighbours.

	With all of the above definitions, we can formalise the
        network aggregative (NA) game as the tuple $\Gamma =
        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$. \fb{preferably use a
          definition environment.}

@@

	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
	Fictitious Play in continuous time.
%
	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
	\end{definition}

@@

	\begin{theorem}
		There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
		BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
	\end{theorem}

@@

	\section{Non-convergent examples}
	The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.

@@

	\section{Addition of Noise}
